\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-09 doc/publications/plos16/plos16.tex
Few more changes to second para of that section

To test whether the associated features have biological meaning, we investigate whether variants in or near
BMD-associated genes are enriched toward the top of our ranked variant list. To form this list of "known genes", we start
with the 26 known BMD genes listed by Duncan {\it et al.}~\cite{Duncan.2011}. We also include the 6 genes that they find
with a new BMD association. We then add to this list the genes that Estrada {\it et al.} found with a new BMD association.
In total, this gives us a list of 100 genes.

@@

We therefore investigate the highest-ranked features not amongst the associated gene list by Duncan
{\it et al.}~\cite{Duncan.2011}. COLEC10 (collectin 10) contains variants more recently associated with
BDM~\cite{Kemp2014,Liu2008}, with a verified transcription factor binding site for the known BMD gene FOXL1~\cite{DECODE}.
%However, we also observe that from the set of highest-ranked features, for example, the top ten, not all of them exist
%within close proximity to known BMD genes. We investigate the literature to determine the plausibility of these variants
%contributing to BMD.
%One gene is COLEC10 (collectin 10). Featuring a transcription factor binding site for FOXL1, COLEC10 is also reported as
%containing variants associated with BMD \cite{Kemp2014,Liu2008}. However there currently exists no information on how this gene
%may contribute to BMD. 
Also highly-ranked are variants in chromosome 22q11. Stagi {\it et al.}~\cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant reduction in bone mass. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by Phang {\it et al.}~\cite{Phang.2008}, proline is made available by collagen degradation.

>>>>

To test whether the associated features have biological meaning, we investigate whether variants in or near
BMD-associated genes are enriched toward the top of our ranked variant list. To form this list of "known genes", we start
with the 26 known BMD genes listed by Duncan {\it et al.}~\cite{Duncan.2011}. We also include the 6 genes that they find
with a new BMD association. We then add to this list the genes that Estrada {\it et al.} found with a new BMD
association~\cite{Estrada2012}. In total, this gives us a list of 100 different genes.

@@

We therefore investigate the highest-ranked features that are not located near genes from our known-gene list. One gene,
COLEC10	 (collectin 10) contains variants more recently associated with
BDM~\cite{Kemp2014,Liu2008}, with a verified transcription factor binding site for the known BMD gene FOXL1~\cite{DECODE}.
%However, we also observe that from the set of highest-ranked features, for example, the top ten, not all of them exist
%within close proximity to known BMD genes. We investigate the literature to determine the plausibility of these variants
%contributing to BMD.
%One gene is COLEC10 (collectin 10). Featuring a transcription factor binding site for FOXL1, COLEC10 is also reported as
%containing variants associated with BMD \cite{Kemp2014,Liu2008}. However there currently exists no information on how this gene
%may contribute to BMD. 
Also highly-ranked are variants in chromosome 22q11. Stagi {\it et al.}~\cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant reduction in bone mass. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by Phang {\it et al.}~\cite{Phang.2008}, proline is made available by collagen degradation.
